\HeaderA{methyl}{NTP bioassay data: effect of methyleugenol on skin fibroma}{methyl}
\keyword{datasets}{methyl}
\begin{Description}\relax
NTP bioassay of methyleugenol: 200 male rats were randomly assigned to 4 treatment groups with balanced sample size 50.
Individuals in treatment group 0, 1, 2, and 3 received doses of 0, 37, 75, and 150 mg methyleugenol per kg body weight, respectively.
The response variable \code{tumour} is the presence of skin fibroma at time of death.
The variable \code{death} gives individual time of death, with a final sacrifice of surviving animals at 730 days after begin of the assay.
\end{Description}
\begin{Usage}
\begin{verbatim}data(methyl)\end{verbatim}
\end{Usage}
\begin{Format}\relax
A data frame with 200 observations on the following 3 variables.
\describe{
\item[\code{group}] a factor with levels \code{0} \code{1} \code{2} \code{3}, specifying dose groups 0, 37, 75, and 150 mg/kg, respectively
\item[\code{tumour}] a numeric vector, specifying whether a tumour was present at time of death
\item[\code{death}] a numeric vector, specifying the time of death
}
\end{Format}
\begin{Source}\relax
National toxicology program (2000).
\end{Source}
\begin{References}\relax
SD Peddada, GE Dinse, JK Haseman (2005): A survival-adjusted quantal response test for comparing tumour incidence rates. Applied Statistics 54, 51-61.
\end{References}
\begin{Examples}
\begin{ExampleCode}
data(methyl)
# raw tumour proportions:
table(methyl[c("group", "tumour")])

# time of death:
boxplot(death~group, data=methyl, horizontal=TRUE)

\end{ExampleCode}
\end{Examples}

